%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1.5pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheadingDetailed}[5]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
      {\small#5} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}


\begin{document}


\begin{center}
    {\Huge \scshape Yash Agarwal} \\ \vspace{1pt}
    % 2098 16th Main Indiranagar Hal Stage 2 Bangalaore Karnataka 560008 \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +91-7982550561 ~ \href{mailto:yagarwal1307@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{yagarwal1307@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/yash-agarwal-5b038a167/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/yash-agarwal-5b038a167}}  ~
    \href{https://github.com/yagarwal-allo}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/yagarwal-allo}}
    \vspace{-8pt}
\end{center}

%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.08in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Typescript, JavaScript, Java, C++, SQL, HTML/CSS, Solidity} \\
     \textbf{Developer Tools}{: AWS, GCP, Redis, Serverless, Terraform, Docker, Kubernetes, IPFS, Web3Storage, Drand } \\
     \textbf{Technologies/Frameworks}{: LLM, NestJS, NextJS, SpringBoot, FastAPI, Django, React, SkLearn, NLTK, Qiskit} \\
    }}
 \end{itemize}
 \vspace{-16pt}



%-----------EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheadingDetailed
      {\href{https://www.allohealth.care/}{Allo Health \faLink\ }}{June 2022 -- Present}
      {Founding Engineer}{Banagalore, Karanataka}
      {- Building an end to end health care delivery platform. Joined as one of the founding engineers.}
      \resumeItemListStart
        \resumeItem{\textbf{AI Copilot --} Project owner of Allo Copilot, an omnichannel clinical assistance copilot:}
          \resumeItemListStart
            \resumeItem{Created and maintained APIs, interfaces, pipelines and infrastructure for the RAG and ReAct powered copilot.}
            \resumeItem{Automated triaging, conversational actioning and prioritised escalations reduced \textbf{90\%} human interventions.}
            \resumeItem{Reduced response time and multilingual responses improved patient satisfaction and increased bookings by  \textbf{20\%}.}
            \resumeItem{\textbf{Exposure:} AWS, LLM, Python, VectorDB, Fast API, NestJS, NextJS, Langchain, ReAct, RAG.}
          \resumeItemListEnd
        \resumeItem{\textbf{EMR, Payments \& Commerce and Teleconsultation Platform --} Core services offered by Allo Health:}
          \resumeItemListStart
            \resumeItem{Created and maintained APIs and infrastructure for services including Scheduler, EMR, Payments \& Commerce.}
            % \resumeItem{Created user interfaces and admin dashboards for patients, doctors and admins using NextJS and Retool.}
            % \resumeItem{Led the development of teleconsultation platform improving conversion by x\% and implemented IVR system to fully automate consultation reminders and handshakes earlier handled by a team of 10 people.}
            \resumeItem{Led the development of teleconsultation platform fully automating the consultation management process. This increased the consultation completion rate by \textbf{30\%} and allowed scaling the operations \textbf{4x} with the same team size.}
            \resumeItem{Led the implementation of authentication system and key contributor in RBAC based authorization system.}
            \resumeItem{\textbf{Exposure:} AWS, NestJS, NextJS, 100ms, Paperform, SpringBoot, MySQL, Exotel, Retool, Auth0, Gupshup.}
          \resumeItemListEnd
        \resumeItem{\textbf{Infrastructure, Platform and Data:}}
          \resumeItemListStart
            \resumeItem{\textbf{Event Driven Architecture:} Used Redis streams \& groups to enable async processing of events and improving the reliability and observability of the events in the system.}    
            \resumeItem{\textbf{Infrastructure as code}: Wrote Terraform, docker and github actions configurations to provision infrastructure and set up CI/CD. Optimized existing CI/CD pipelines to reduce deployment times and costs by \textbf{60\%}}
            % \resumeItem{Created tools to \emph{fully automate} data extraction and dashboard creation eliminating all the manual efforts.} 
            \resumeItem{\textbf{DataOps}: Developed a tool to \emph{fully automate} data extraction pipeline by allowing users to schedule queries which on execution dumped data in google sheets, eliminating \textbf{90\%} of the manual efforts.}
            % \resumeItem{Wrote migration scripts to ensure data integrity and backfill data.}   
            % \resumeItem{Implemented feature flags to enable feature management \& toggling and A/B testing.}
            \resumeItem{\textbf{Exposure:} AWS, GCP, Python, Redis, Github Actions, Docker, Terraform, Harness, Feature Flag}
          \resumeItemListEnd
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://www.mtxb2b.com/}{MTX Group \faLink\ }}{May 2021 -- Aug 2021}
      {Software Engineer Intern}{Hyderabad, Telangana}
      \resumeItemListStart
        \resumeItem{\textbf{Notification Service:} Built a consumer listener architecture based highly available sms notification and chatbot service improving response time by \textbf{40\%} and engagement by \textbf{20\%}.}
        \resumeItem{\textbf{Component Library:} Created a sharable library for AngularJS components using StoryBook.}
        \resumeItem{Awarded PPO for exceptional performance and contribution to the company.}
        \resumeItem{\textbf{Exposure:} \emph{Spring Boot, Kafka, Twilio, MongoDB, NestJS, AngularJS, StoryBook, NPM.} }
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-13pt}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {IIT (BHU) Varanasi}{July 2018 -- May 2022}
      {Bachelor of Technology (9.16 CGPA)}{Varanasi, Uttar Pradesh}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\href{https://github.com/yagarwal-allo/timecapsule}{\underline{\textbf{Timecapsule - A responsible vulnerability discloser}}} $|$ \emph{NestJS, IPFS, Drand, Web3 Storage}}{May 2023}
          \resumeItemListStart
            \resumeItem{A tool to enable security researchers to time-lock the discovered vulnerabilities and responsibly disclose them later.}
          \resumeItemListEnd 
          \vspace{-17pt}
      \resumeProjectHeading
          {\href{https://github.com/dhritimaandas/Traffic_Sign_Recog_Inter_IIT}{\underline{\textbf{Traffic Signal Recognition - Bosch}}} $|$ \emph{NextJS, Flask, Google Firebase}}{Mar 2021}
          \resumeItemListStart
            \resumeItem{Lead a team of 4 to an ETL tool to enable continuous training, deployment and monitoring of deep learning model.}
          \resumeItemListEnd
          \vspace{-17pt}
      \resumeProjectHeading
          {\textbf{Dream 11 Team Predictor} $|$ \emph{Python, Sklearn, Beautiful Soup}}{Sept 2020}
          \resumeItemListStart
            \resumeItem{Trained a model to predict the best Dream 11 team for a given match. Accuracy wasn't great but it was fun to build.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}

%
%-----------PROGRAMMING SKILLS-----------
\section{Extracurricular}
\begin{itemize}[leftmargin=0in, label={}]
   \small{\item{
    {$\vcenter{\hbox{\tiny$\bullet$}}$}  \emph{Quantum Explorers, IBM} -- Part of 2023 Cohort of Quantum explorers to learn and explore Quantum Computing. \\
    {$\vcenter{\hbox{\tiny$\bullet$}}$}  \emph{Open Source Contributor} -- Actively contributed to many open source projects like Meshery, OpenCopilot, Qiskit etc. \\
    {$\vcenter{\hbox{\tiny$\bullet$}}$}  \emph{Gold Medalist Inter-IIT '21} -- Product case study to automate payout process of Kaching.  \\
    {$\vcenter{\hbox{\tiny$\bullet$}}$}  Led organisations at IIT (BHU) to organise events, workshops and case studies for 200+ students throughout the year. \\
    {$\vcenter{\hbox{\tiny$\bullet$}}$}  Participated in and won various other prestigious case study competitions. \\
    {$\vcenter{\hbox{\tiny$\bullet$}}$}  Interned in Equity Research, Data Science and Product roles to develop business acumen and financial analysis skills.  \\
   }}
\end{itemize}
\vspace{-16pt}

\end{document}
